\pkg{shorts}: An R Package for Modeling Short Sprints

### 2020-10-20 paper.Rmd
Reformat

options("width" = 80)

knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = FALSE,
  fig.retina = 0.8, # figures are either vectors or 300 dpi diagrams
  dpi = 600,
  out.width = "90%",
  fig.align = "center",
  fig.width = 6,
  fig.height = 6 * 0.618, # 1 / phi
  fig.show = "hold",
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  width = 80
)

@@

# Set rounding
op <- options()
options(digits = 2)
```

@@

kinematics_long <- kinematics %>%
  pivot_longer(
    cols = c("distance", "velocity", "acceleration"),
    names_to = "variable"
  ) %>%
  mutate(
    variable = factor(
      variable,
      levels = c("distance", "velocity", "acceleration"),
      labels = c(
        expression("Distance (m"*")"),
        expression("Velocity (ms"^-1*")"),
        expression("Acceleration (ms"^-2*")"))
    )
  )

gg <- ggplot(
  kinematics_long,
  aes(x = time, y = value, color = Athlete)
) +
  theme_bw() +
  geom_line(alpha = 0.7) +
  facet_wrap(
    ~variable,
    scales = "free_y",
    labeller = label_parsed) +
  ylab(NULL) +
  xlab("Time (s)") +
  theme(legend.position = "top", legend.title = element_blank())

@@

```{r four-athletes-profile, echo=FALSE, fig.cap="Acceleration-Velocity profile of four athletes with different MSS and MAC parameters."}
gg <- ggplot(
  kinematics,
  aes(x = velocity, y = acceleration, color = Athlete)
) +
  theme_bw(10) +
  geom_line(alpha = 0.7) +
  ylab(expression("Acceleration (ms"^-2*")")) +
  xlab(expression("Velocity (ms"^-1*")")) +
  theme(legend.position = "top", legend.title = element_blank())

@@

ggplot(df, aes(x = distance)) +
  theme_bw(10) +
  geom_line(aes(y = time)) +
  geom_point(aes(y = pred_time), color = "red") +
  xlab("Distance (m)") +
  ylab("Time (s)")
```

@@

ggplot(df, aes(x = distance, y = value)) +
  theme_bw(10) +
  facet_wrap(~name, scales = "free_y") +
  geom_line(alpha = 0.7) +
  ylab(NULL) +
  xlab("Distance (m)")
```

@@

ggplot(
  filter(df, distance < 40),
  aes(x = distance, y = value, group = athlete, color = athlete)
) +
  theme_bw(10) +
  facet_wrap(~name, scales = "free_y") +
  geom_line(alpha = 0.7) +
  ylab(NULL) +
  xlab("Distance (m)") +
  theme(legend.position = "top", legend.title = element_blank())
```

@@

# Generate velocity by using:
# round(predict_velocity_at_time(time = sprint_time, MSS = 9, TAU = 1.3), 2)

@@

ggplot(plot_df, aes(x = value, y = velocity, color = `Sync issue`)) +
  theme_bw(10) +
  geom_line(alpha = 0.7) +
  xlab("Time (s)") +
  ylab(expression("Velocity ("*ms^-1*")"))
```

@@

```{r}
# Using the true time
round(
  predict_velocity_at_time(
    time = df$`true time`,
    MSS = m5$parameters$MSS,
    TAU = m5$parameters$TAU
  ),
  2
)

# Using time with sync issues
round(
  predict_velocity_at_time(
    time = df$`0.5s added`,
    MSS = m8$parameters$MSS,
    TAU = m8$parameters$TAU,
    time_correction = m8$parameters$time_correction
  ),
  2
)
```

@@

ggplot(plot_df, aes(x = distance, y = time, color = athlete, group = athlete)) +
  theme_bw() +
  geom_point() +
  geom_line() +
  xlab("Distance (m)") +
  ylab("Time (s)")
```

@@

round(sprint_parameters, 2)
```

@@

head(round(sim_df, 2))
```

@@

# MSS
ggplot(df, aes(x = flying_start_distance, y = est_MSS, color = MAC_string)) +
  theme_bw() +
  geom_line(alpha = 0.7) +
  facet_wrap(~MSS_string, scales = "free_y") +
  xlab("Flying start distance (m)") +
  ylab("estimated MSS (m/s)") +
  theme(legend.title = element_blank())
```

@@

```{r}
# MAC
ggplot(df, aes(x = flying_start_distance, y = est_MAC, color = MSS_string)) +
  theme_bw() +
  geom_line(alpha = 0.7) +
  facet_wrap(~MAC_string, scales = "free_y") +
  xlab("Flying start distance (m)") +
  ylab("estimated MAC (m/s/s)") +
  theme(legend.title = element_blank())
```

@@

```{r}
# PMAX
ggplot(df, aes(x = flying_start_distance, y = est_PMAX, color = MSS_string)) +
  theme_bw() +
  geom_line(alpha = 0.7) +
  facet_wrap(~MAC_string, scales = "free_y") +
  xlab("Flying start distance (m)") +
  ylab("estimated PMAX (W/kg)") +
  theme(legend.title = element_blank())
```

@@

ggplot(model_df, aes(y = residuals, x = distance, color = flying_start_distance, group = group)) +
  theme_bw() +
  geom_line(alpha = 0.3) +
  facet_grid(MSS_string ~ MAC_string) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_gradientn(colours = terrain.colors(5, rev = FALSE)) +
  xlab("Distance (m)") +
  ylab("Predicted time - observed time (s)")
```

@@

```{r}
ggplot(model_df, aes(y = residuals, x = distance, color = flying_start_distance, group = group)) +
  theme_bw() +
  geom_line(alpha = 0.3) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_gradientn(colours = terrain.colors(5, rev = FALSE)) +
  xlab("Distance (m)") +
  ylab("Predicted time - observed time (s)")
```

@@

ggplot(model_df, aes(y = residuals, x = distance, color = flying_start_distance, group = group)) +
  theme_bw() +
  geom_line(alpha = 0.3) +
  facet_wrap(~model) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_gradientn(colours = terrain.colors(5, rev = FALSE)) +
  xlab("Distance (m)") +
  ylab("Predicted time - observed time (s)")
```

@@

ggplot(model_df, aes(y = residuals, x = distance, color = time_lag, group = group)) +
  theme_bw() +
  geom_line(alpha = 0.3) +
  facet_wrap(~model) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_gradientn(colours = terrain.colors(5, rev = FALSE)) +
  xlab("Distance (m)") +
  ylab("Predicted time - observed time (s)")
```

@@

head(round(sim_df, 2))
```

@@

ggplot(model_df, aes(y = residuals, x = distance, color = displacement, group = group)) +
  theme_bw() +
  geom_line(alpha = 0.3) +
  facet_wrap(~model) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_gradientn(colours = terrain.colors(5, rev = FALSE)) +
  xlab("Distance (m)") +
  ylab("Predicted time - observed time (s)")
```

@@

ggplot(df, aes(x = value)) +
  theme_bw() +
  geom_boxplot() +
  facet_wrap(~parameter, scales = "free_x") +
  xlab(NULL) +
  ylab(NULL) +
  theme(
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  )
```

@@

ggplot(df, aes(x = distance, y = resid, color = name)) +
  theme_bw() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point() +
  theme(legend.title = element_blank()) +
  xlab("Distance (m)") +
  ylab("Predicted - observed time (s)")
```

@@

rownames(bolt_model) <- bolt_model$model

round(bolt_model[-1], 3)
```

@@

ggplot(model_fit, aes(x = RSE, y = model)) +
  theme_bw() +
  geom_point() +
  xlab("RSE (s)") +
  ylab(NULL)
```

>>>>

options("width" = 60)

knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = FALSE,
  fig.retina = 0.8, # figures are either vectors or 300 dpi diagrams
  dpi = 600,
  out.width = "100%",
  fig.align = "center",
  fig.width = 6,
  fig.height = 6 * 0.618, # 1 / phi
  fig.show = "hold",
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  width = 60
)

@@

# Set rounding
op <- options()
options(digits = 3)
```

@@

kinematics_long <- kinematics %>%
  pivot_longer(
    cols = c("distance", "velocity", "acceleration"),
    names_to = "variable"
  ) %>%
  mutate(
    variable = factor(
      variable,
      levels = c("distance", "velocity", "acceleration"),
      labels = c(
        expression("Distance (m" * ")"),
        expression("Velocity (ms"^-1 * ")"),
        expression("Acceleration (ms"^-2 * ")")
      )
    )
  )

gg <- ggplot(
  kinematics_long,
  aes(x = time, y = value, color = Athlete)
) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_wrap(
    ~variable,
    scales = "free_y",
    labeller = label_parsed
  ) +
  ylab(NULL) +
  xlab("Time (s)") +
  theme(legend.position = "top", legend.title = element_blank())

@@

```{r four-athletes-profile, echo=FALSE, fig.cap="Acceleration-Velocity profile of four athletes with different MSS and MAC parameters."}
gg <- ggplot(
  kinematics,
  aes(x = velocity, y = acceleration, color = Athlete)
) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  ylab(expression("Acceleration (ms"^-2 * ")")) +
  xlab(expression("Velocity (ms"^-1 * ")")) +
  theme(legend.position = "top", legend.title = element_blank())

@@

ggplot(df, aes(x = distance)) +
  theme_bw(8) +
  geom_line(aes(y = time)) +
  geom_point(aes(y = pred_time), color = "red") +
  xlab("Distance (m)") +
  ylab("Time (s)")
```

@@

ggplot(df, aes(x = distance, y = value)) +
  theme_bw(8) +
  facet_wrap(~name, scales = "free_y") +
  geom_line(alpha = 0.7) +
  ylab(NULL) +
  xlab("Distance (m)")
```

@@

ggplot(
  filter(df, distance < 40),
  aes(x = distance, y = value, group = athlete, color = athlete)
) +
  theme_bw(8) +
  facet_wrap(~name, scales = "free_y") +
  geom_line(alpha = 0.7) +
  ylab(NULL) +
  xlab("Distance (m)") +
  theme(legend.position = "top", legend.title = element_blank())
```

@@

@@

ggplot(plot_df, aes(x = value, y = velocity, color = `Sync issue`)) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  xlab("Time (s)") +
  ylab(expression("Velocity (" * ms^-1 * ")"))
```

@@

```{r}
# Using the true time
predict_velocity_at_time(
  time = df$`true time`,
  MSS = m5$parameters$MSS,
  TAU = m5$parameters$TAU
)

# Using time with sync issues
predict_velocity_at_time(
  time = df$`0.5s added`,
  MSS = m8$parameters$MSS,
  TAU = m8$parameters$TAU,
  time_correction = m8$parameters$time_correction
)
```

@@

ggplot(plot_df, aes(x = distance, y = time, color = athlete, group = athlete)) +
  theme_bw(8) +
  geom_point() +
  geom_line() +
  xlab("Distance (m)") +
  ylab("Time (s)")
```

@@

sprint_parameters
```

@@

head(sim_df)
```

@@

# MSS
ggplot(df, aes(x = flying_start_distance, y = est_MSS, color = MAC_string)) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_wrap(~MSS_string, scales = "free_y") +
  xlab("Flying start distance (m)") +
  ylab("estimated MSS (m/s)") +
  theme(legend.title = element_blank())
```

@@

```{r}
# MAC
ggplot(df, aes(x = flying_start_distance, y = est_MAC, color = MSS_string)) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_wrap(~MAC_string, scales = "free_y") +
  xlab("Flying start distance (m)") +
  ylab("estimated MAC (m/s/s)") +
  theme(legend.title = element_blank())
```

@@

```{r}
# PMAX
ggplot(df, aes(x = flying_start_distance, y = est_PMAX, color = MSS_string)) +
  theme_bw(8) +
  geom_line(alpha = 0.7) +
  facet_wrap(~MAC_string, scales = "free_y") +
  xlab("Flying start distance (m)") +
  ylab("estimated PMAX (W/kg)") +
  theme(legend.title = element_blank())
```

@@

ggplot(model_df, aes(y = residuals, x = distance, color = flying_start_distance, group = group)) +
  theme_bw(8) +
  geom_line(alpha = 0.3) +
  facet_grid(MSS_string ~ MAC_string) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_gradientn(colours = terrain.colors(5, rev = FALSE)) +
  xlab("Distance (m)") +
  ylab("Predicted time - observed time (s)")
```

@@

```{r}
ggplot(model_df, aes(y = residuals, x = distance, color = flying_start_distance, group = group)) +
  theme_bw(8) +
  geom_line(alpha = 0.3) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_gradientn(colours = terrain.colors(5, rev = FALSE)) +
  xlab("Distance (m)") +
  ylab("Predicted time - observed time (s)")
```

@@

ggplot(model_df, aes(y = residuals, x = distance, color = flying_start_distance, group = group)) +
  theme_bw(8) +
  geom_line(alpha = 0.3) +
  facet_wrap(~model) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_gradientn(colours = terrain.colors(5, rev = FALSE)) +
  xlab("Distance (m)") +
  ylab("Predicted time - observed time (s)")
```

@@

ggplot(model_df, aes(y = residuals, x = distance, color = time_lag, group = group)) +
  theme_bw(8) +
  geom_line(alpha = 0.3) +
  facet_wrap(~model) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_gradientn(colours = terrain.colors(5, rev = FALSE)) +
  xlab("Distance (m)") +
  ylab("Predicted time - observed time (s)")
```

@@

head(sim_df, 2)
```

@@

ggplot(model_df, aes(y = residuals, x = distance, color = displacement, group = group)) +
  theme_bw(8) +
  geom_line(alpha = 0.3) +
  facet_wrap(~model) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  scale_color_gradientn(colours = terrain.colors(5, rev = FALSE)) +
  xlab("Distance (m)") +
  ylab("Predicted time - observed time (s)")
```

@@

ggplot(df, aes(x = value)) +
  theme_bw(8) +
  geom_boxplot() +
  facet_wrap(~parameter, scales = "free_x") +
  xlab(NULL) +
  ylab(NULL) +
  theme(
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()
  )
```

@@

ggplot(df, aes(x = distance, y = resid, color = name)) +
  theme_bw(8) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point() +
  theme(legend.title = element_blank()) +
  xlab("Distance (m)") +
  ylab("Predicted - observed time (s)")
```

@@

bolt_model
```

@@

ggplot(model_fit, aes(x = RSE, y = model)) +
  theme_bw(8) +
  geom_point() +
  xlab("RSE (s)") +
  ylab(NULL)
```
